Pipit: Reactive Systems in \fstar ~(Extended Abstract)

### 2023-05-10 2023pipit/Main.tex
ok

XXX show k-inductive proof of $bibo_3$?
\begin{verbatim}
// CLEAN
let fir_prop_prove (fv: sem_freevars): Lemma (ensures induct2 (bibo3 fv)) =
  assert (base_case\_2 (bibo3 fv)) by (tac_nbe (); tac_intros_smash (); tac_nbe ());
  assert (step_case\_2 (bibo3 fv)) by (tac_nbe (); tac_intros_smash (); tac_nbe ())
\end{verbatim}

>>>>

XXX show k-inductive proof of $bibo_3$?
\begin{verbatim}
let fir_prop_prove (fv: sem_freevars): Lemma (ensures induct2 (bibo3 fv)) =
  assert (base_case2 (bibo3 fv)) by (tac_nbe (); tac_intros_smash (); tac_nbe ());
  assert (step_case2 (bibo3 fv)) by (tac_nbe (); tac_intros_smash (); tac_nbe ())
\end{verbatim}
